Using traffic analysis to identify The Second Generation Onion Router

### 2011-06-13 ieee-conference-paper/paper.tex
IEEE biblatex, describe why not using any sorting
More details in experiment section, versions of software, dates of phases

% Use biblatex with IEEE style
\RequirePackage[american]{babel}
\RequirePackage{csquotes}

% Use the excellent biblatex package with apa style
% minnames=1,maxnames=2 - abbreviates all author names in citations
% hyperref - links in pdf
\RequirePackage[
  sorting = none,
  url = false,
  hyperref = true,
  style = ieee,
  bibencoding = utf8]{biblatex}
\DeclareLanguageMapping{american}{american-apa}

@@

To determine if Tor traffic can be distinguished from regular encrypted
traffic, an experiment was conducted to generate a series of traces for
comparison. HTTPS traffic was generated using the commonly available Firefox
browser, with a series of typical user interactions simulated with the Selenium
browser testing framework. The same simulations were run through a simulated
Tor network using both the HTTP and HTTPS protocol.

The experiment was run over the course of 8 weeks yielding three sets of sample
data:

>>>>

% Use the excellent biblatex package with IEEE style, sorted = none makes the numbering appear in order
\RequirePackage[american]{babel}
\RequirePackage{csquotes}
\RequirePackage[
  sorting = none,
  url = false,
  hyperref = true,
  style = ieee,
  bibencoding = utf8]{biblatex}
\DeclareLanguageMapping{american}{american-apa}

@@

To determine if Tor traffic can be distinguished from regular encrypted
traffic, an experiment was conducted to generate a series of traces for
comparison. Network traffic was generated using the commonly available Firefox
browser, version 3.6.8 installed on an Ubuntu 10.04 desktop operating system.
One hundred and seventy simulations were run of varied user interactions
against a sample of thirty websites, using version 1.0.6 of the Selenium
Browser testing framework. A private Tor network was configured running three
directory servers and fifteen relays, with version 0.2.1.26.

The experiment consisted of three phases, the first was the capture of regular
HTTPS traffic which began Sunday the 3rd of October 2010 and finished Sunday
the 17th that same month. Phase two began immediately after and continued two
weeks till the 31st of October. This phase involved capturing regular HTTP
traffic routed through a private Tor network. The final phase began on the 7th
of November and concluded on the 21st, this phase was the capture of HTTPS
traffic through a private Tor network.

To reduce the affect of confounding variables, all phases conducted the same
simulations, on an isolated test network and were conducted within a virtual
machine snapshot which was periodically rolled back to a clean, known state.
The experiment yielded three sets of sample data:
